Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Weather pipeline execution times
Wrap figure

In order to expose data parallelism from the output of a command,
files that don't point to a resource can have an upper bound on the
lines that they can tranfer. This can be useful to utilize avaliable
parallelism after encountering a command that cannot be parallelized
(e.g. \ttt{sha1sum}). The following example illustrates this scenario.

\includegraphics[width=0.40\columnwidth]{\detokenize{./figs/dish_g2.pdf}}

>>>>

In order to expose data parallelism from the output of a command, files that
don't point to a resource can have
\begin{wrapfigure}[3]{r}{0.20\columnwidth}
\vspace{-7pt}
  \includegraphics[width=0.20\columnwidth]{\detokenize{./figs/dish_g2.pdf}}
\vspace{-20pt}
\end{wrapfigure}
an upper bound on the lines that they can transfer. This can be useful to utilize available
parallelism after encountering a command that cannot be parallelized
(\eg \ttt{sha1sum}). The schematic on the right illustrates this scenario.
